%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
  	{ASOS.com} % Organization
    {Platform Engineer} % Job title
    {Belfast, Northern Ireland} % Location
    {Jul. 2023 - Present} % Date(s)
    {
    \begin{cvitems}
		\item {A first promotion of all associate engineers in ASOS NI, leased to two teams providing consulting platform support.}
		\item {Routinely assisting and providing platform guidance for over new solutions (e.g., Databricks Lakehouse) and existing platform health.}
		\item {Build highly modular CI/CD pipelines and migrating existing Teamcity solutions to Azure DevOps.}
        \item {\textbf{Key Skills:} Azure (+\textbf{DevOps}), \textbf{Powershell}, \textbf{ARM/Bicep}, \textbf{ADLS}, Problem Solving, Agile, Consulting Support}
     \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  	{ASOS.com} % Organization
    {Associate Platform Engineer} % Job title
    {Belfast, Northern Ireland} % Location
    {Mar. 2022 - Jul. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led efforts to secure and optimise \textbf{CI/CD} in a number of solutions, and bring them to source, reducing deployment times by up-to \textbf{60\%}.}
        \item {Provisioned new development environments and securely implemented solutions with \textbf{Azure DevOps} and \textbf{IaC} (e.g., Bicep).}
        \item {Developed a fully \textbf{automated} solution for querying and applying patches with \textbf{Azure Pipelines} and Powershell.}
        \item {Spearheaded \textbf{agile} ceremonies and took \textbf{initiative} in solving issues with infrastructure and \textbf{release} processes for \textbf{different teams}.}
        \item {Played key part in a \textbf{cost-optimisation} strategy, where my proposals saved the company \textbf{\approx £10k/mo} on infrastructure optimisation.}
        %\item {Developed a pipeline for avoiding scheduled maintenance, by switching databases to another node, which reduced maintenance time by three-fold.}
        %\item {Contributed to Grafana monitoring \textbf{migration} from the on-prem solution to Azure; and improved the scope of existing \textbf{monitoring} solutions by using Azure Log Analytics and \textbf{KQL} for creating alerts.}
		\item {Built Logic App infrastructure for hosting workflows logging databases, and improved the scope of existing \textbf{monitoring} solutions.}
%        \item {Built Logic App infrastructure for hosting workflows logging databases, and improved the scope of existing \textbf{monitoring} solutions by using Azure Log Analytics and \textbf{KQL}.}
        %\item {Led efforts on developing new DevOps self-hosted build agents, in both \textbf{configuration managed} VMs and container variations.}
        %\item {Pioneering in \textbf{building CI/CD infrastructure} for new generation, Databricks-based solution to improve data scallability.}
        \item {\textbf{Key Skills:} Azure (+\textbf{DevOps}), \textbf{Powershell (+DSC)}, \textbf{ARM/Bicep}, Bash, KQL, REST APIs, Git, Problem Solving, Agile, Teamplaying}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  	{South Eastern Regional College / ASOS.com} % Institution
    {Data Engineering Academy Trainee} % Degree
    {Bangor, Northern Ireland} % Location
    {Jan. 2022 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Successfully passed an intensive 10-week academy, conducted via the Department for the Economy employment programme.}
        %\item {\textbf{Proactively} supported my colleagues during both independent and group work.}
        \item {Passed two Azure Fundamentals exams in rapid succession and was offered a permanent position at ASOS.com following an interview.}
        \item {\textbf{Key Skills:} C\#, T-SQL, Azure (Fundamentals), Mentoring, Collaboration, Presentations, Teamwork}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Queen's University Belfast} % Organization
    {Postgraduate Researcher (Astrophysics)} % Job title
    {Belfast, Northern Ireland} % Location
    {Oct. 2019 - Feb 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {Part of QUB's Astrophysics Research Centre, supporting research towards the ESA planetary defence mission Hera.}
        \item {Processed spectroscopic data with pipelines and state-of-the-art statistical methods; undertook training in \textbf{Python}, statistics and scientific computing including HPC with Numba via the Nvidia DLI scheme.}
        \item {Collaboratively planned, supported and executed astronomical observations on world-renowned 8m class telescopes.}
        %\item {Authored (and co-authored) two abstracts for the 7th IAA Planetary Defense Conference respectively.}
        \item {\textbf{Key Skills:} Python (NumPy, Pandas, AstroPy, Numba), Research, Project Management, Statistics, Teamwork, Presentations, \LaTeX}
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
  \cventry
  	{Queen's University Belfast} % Organization
    {Graduate Teaching Assistant} % Job title
    {Belfast, Northern Ireland} % Location
    {Sep. 2019 - Feb 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {Assisted delivery of four modules within the School of Mathematics and Physics,  beyond my contracted duties as a researcher.}
        \item {Co-led workshops and supported Physics undergraduate students, ranging from laboratory to computing classes.}
        \item {Proactively helped struggling students by giving them \textbf{tutoring in coding}, who subsequently passed the module.}
        \item {\textbf{Key Skills:} Python, Communication, Mentoring, Presentations, \LaTeX} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  	{BAE Systems (via SEPNet scheme)} % Organization
    {AI Engineer} % Job title
    {Filton, England} % Location
    {Jul. 2018 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {Interned as part of the AI group, working on novel image detection algorithms with LSTMs and GRUs.}
        \item {Improved the efficiency of the key machine learning model \textbf{by 20\%} by implementing GRUs to an existing ML codebase.}
        \item {Presented improvements to directors, and at a subsequent conference in London.}
        \item {\textbf{Key Skills:} Python (\textbf{Tensorflow}), Git, Presenting, Collaboration}
      \end{cvitems}
    }
%---------------------------------------------------------

\cvparagraph{\textbf{+} Under a year of casual experience including Seasonal Mail Sorter at Royal Mail and Open Day Ambassador for University of Kent.}

\end{cventries}


