%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations \& Appearances}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  	{Presentation: Reproducible Code Practices} %Role
  	{ReproducabiliTea Network} %Affiliation
    {Belfast, UK} % Location
    {Mar. 2023} % Date(s)
   {
      \begin{cvitems} % Description(s)
        \item A talk about DevOps practices for a local University. Uploaded slides to the \href{https://osf.io/yma2d}{\textbf{Open Science Framework}}.
        \item Focused on aspects of reproducible code, and practical insights from industry on DevOps culture and techniques.
      \end{cvitems}
    }

%---------------------------------------------------------
%  \cventry
%    {Presentation: AIDA - Where Activism Meets Asteroids} 
%    {NI Science Festival 2021} 
%    {Queen's University Belfast} % Location
%    {Feb. 2020} % Date(s)
%    {
%      \begin{cvitems} % Description(s)
%        \item A public lecture about Planetary Defence and involvement of QUB in ESA Hera and other ground based observation programmes.
%      \end{cvitems}
%    }
    
 %---------------------------------------------------------
  \cventry
	{Presentation: Investigating AI Techniques}
    {SEPnet 10th Student Exhibition Fair} 
    {London, UK} % Location
    {Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item \href{https://kiersz.dev/src/resources/bae-poster.pdf}{\textbf{Showcased}} my AI research on use of GRUs for detecting real-time image patterns. Attended on behalf of BAE Systems.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\cvsubsection{Other Appearances}

\begin{cvminortalks}

%   \cvminortalk
%   	{Sync NI - Trailblazers}
%    {Author}
%    {Online} % Location
%    {Mar. 2023} % Date(s)$

   \cvminortalk
    {\href{https://podcasters.spotify.com/pod/show/firedev/episodes/FireDEV-23---Dominik-Kiersz-Programmer-For-One-Of-the-UKs-Largest-Online-Retailers-ASOS-e1tvvvr}{Firedev Podcast - Episode 23}}
    {Invitee}
    {Online} % Location
    {Mar. 2023} % Date(s)
    
    \cvminortalk
   	{NI Assured Skills Academy - ASOS Cohort 2 Induction}
    {Guest Speaker}
    {Belfast, UK} % Location
    {May 2022} % Date(s)    
    
    \cvminortalk
   	{SpecialisterneNI}
    {Guest Speaker (on behalf of ASOS Plc.)}
    {Belfast, UK} % Location
    {Apr. 2022} % Date(s)
   
    \cvminortalk
   	{\href{https://kiersz.dev/src/resources/aida-presentation.pdf}{NI Science Festival 2021}}
    {Presentation: AIDA - Where Activism Meets Asteroids}
    {Belfast, UK} % Location
    {Feb. 2020} % Date(s)
   

\end{cvminortalks}