%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Significant Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Co-lead Developer} % Affiliation/role
    {MOTES (Modular and Optimal Tracer and Extractor of Spectra)} % Organization/group
    {UK} % Location
    {Dec. 2020 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Co-developed a \href{https://github.com/tseccull/motes}{\textbf{Python} application} to process astronomical 2D spectrographs. Developed an optimal extraction routine improving spectral sensitivity by up to one astronomical magnitude.
        \item Exercised \textbf{DevOps} principles to provide documentation, refactoring and\textbf{ CI/CD} with GH Actions.
        \item A dedicated \textbf{software paper} currently in-prep. The package so far contributed to two scientific papers and two conference proceedings.
      \end{cvitems}
    }



%---------------------------------------------------------


   \cventry
   	{Personal Websites}
  	{\href{https://kiersz.dev/}{kiersz.dev} \& \href{https://somethingstochastic.com/}{somethingstochastic.com}}
    {} % Location
    {} % Date(s)
   	{
   	   	\begin{cvitems} 
   	    \item A personal front-page and a blog developed from scratch using Bootstrap CSS framework, and \textbf{Hugo} for the latter.
   	    \item Built infrastructure (\textbf{Terraform}, \textbf{Azure Static Web Apps}) and CI/CD with \textbf{GH Actions} required for website's infrastructure and updates. 
   	    \item Updates to my blog and this CV are \textbf{automatically} reflected on respective websites after merging.
   	    \end{cvitems}
   	}
   	
%---------------------------------------------------------
   	

  \cventry
   	{Personal Project}
    {Homelab}
    {} % Location
    {} % Date(s)
    {
     \begin{cvitems} 
     	\item Researched and built my own home server, that runs a number VMs and containers on \textbf{Proxmox} Type I hypervisor. It provides constant services and content across my home (e.g., Jellyfin, Calibre, Pihole). 
     	\item The infrastructure was built with \textbf{Packer}, \textbf{Terraform} and \textbf{Ansible} for host VMs; and \textbf{Docker-compose} for containerised services. This homelab also utilises UPS control for automatic shutdown and hosts a ADS-B radar station.
     \end{cvitems}
     }
     

%---------------------------------------------------------

  \cventry
    {Contributor} % Affiliation/role
    {FORRT (Framework for Open and Reproducible Research Training)} % Organization/group
    {UK} % Location
    {Jun. 2021 - Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
		\item One of the contributors to the FORRT glossary project and contributed definitions for \textbf{computing, software} and \textbf{statistics}. 
		\item A co-author on the following publication: Parsons, S., Azevedo, F., Elsherif, M. M., Guay, S., Shahim, O. N., Govaart, G. H., … \textbf{Kiersz, D.A.,} ... \& Aczel, B. (2022). \textbf{\href{https://www.nature.com/articles/s41562-021-01269-4}{A Community-Sourced Glossary of Open Scholarship Terms}}. \textit{Nature Human Behaviour}, 6(3), 312-318
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
